External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-28 CVPR2017_Review_Unified.tex
add

In this section, we evaluate the performance of the proposed algorithm on real image denoising. To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior. This will be discussed in Section 4.2. We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage}.

\subsection{The Testing Datasets}
The comparisons are performed on three standard datasets, in which the images were captured by different types of cameras and camera settings under indoor and outdoor lighting conditions. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed for comparison. Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts including different contents. Some samples are shown in Figure \ref{fig4}. The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}. The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}. Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed.

\begin{figure}[t]
\centering
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
\end{minipage}
}\vspace{-0.14in}
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
\end{minipage}
}
\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
\label{fig4}
\end{figure}

@@

\subsection{Implementation Details}
Our proposed method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage. In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM). We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$. We extracted about 3.6 million PGs from the Kodak PhotoCD Dataset, which includes 24 high quality color images, to train the external prior via PG-GMM. In the denoising stage, the paramter $\lambda = 0.002$ is used to regularize the sparse term. The $\delta$ in iterative regularization is set as $\delta = 0.09$. Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$. It is time-consumming to search patch groups (PG) for local patches one by one. To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. Hence, we do not need do distance measure for each local patch.

\subsection{Comparison on External and Internal methods}
In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising. The three methods are evaluated on the dataset provided in \cite{crosschannel2016}. We compare the PSNR and visual quality of these three methods. We also compare the speed. The PSNR and SSIM results on 60 cropped images from \cite{crosschannel2016} are listed in Table 1. The images are cropped into size of $500\times 500$ for better illustration. We also compare the three methods on visual quality in Figure \ref{fig2}. Compare the denoised images listed in Figure \ref{fig2} and Figure \ref{fig2}, we can see that the Offline method is better at edges, smooth regions while the Online method is good at complex textures. The reason is two folds. Firstly, the Offline method is learned on clean images and hence is better at representing edges, structuals, and smooth area. The online method is influenced by the noise and hence some noise cannot be removed. Secondly, the Online method is better at recovering complex area sicne they could learn adaptive dictionaries for the specific area. The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.

\begin{table}\label{tab1}
\caption{Average PSNR(dB) results of External, Internal, and Guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Guided}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9691}
%\\
%\hline
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Comparison With other Competing Methods}
We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}. We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.  The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly. All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image. The NeatImage will fail to perform automatical parameters settings if there is no uniform regions. \footnote{To compare with CCNoise, we first transform the denoised images into double format.}

@@

{
\small
\bibliographystyle{unsrt}
\bibliography{egbib}
}

>>>>

In this section, we evaluate the performance of the proposed algorithm on real image denoising. To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior. This will be discussed in Section 4.3. We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage} in Section 4.4..

\subsection{The Testing Datasets}
The comparisons are performed on three standard datasets, in which the images were captured by different types of cameras and camera settings under indoor and outdoor lighting conditions. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed for comparison. Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts including different contents. Some samples are shown in Figure \ref{fig4}. The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}. The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}. Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed  for comparison.

\begin{figure}[t]
\centering
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
\end{minipage}
}\vspace{-0.14in}
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
\end{minipage}
}
\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
\vspace{-4mm}
\label{fig4}
\end{figure}

@@

\subsection{Implementation Details}
Our proposed method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage. In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM). We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$. We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.

In the external prior guided internal learning stage, there are 4 parameters: $r$ is the number of internal atoms in the learned orthogonal dictionaries, $\lambda$ is the sparse regularization parameter, $T$ the number of iterations for alternative solving problem (\ref{equ5}), and $IteNum$ the number of iterations for denoising algorithm Alg. 1. We set $r=3p^2/2=54$ to treat equally for external and internal priors.We set $\lambda=0.001$, $T=2$, and $IteNum=4$ for our experiments.

\subsection{Comparison with External and Internal Priors}
In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising. The three methods are evaluated on the dataset provided in \cite{crosschannel2016}. We compare the PSNR and visual quality of these three m ethods. We also compare the speed. The PSNR and SSIM results on 60 cropped images from \cite{crosschannel2016} are listed in Table 1. The images are cropped into size of $500\times 500$ for better illustration. We also compare the three methods on visual quality in Figure \ref{fig2}. Compare the denoised images listed in Figure \ref{fig2} and Figure \ref{fig2}, we can see that the Offline method is better at edges, smooth regions while the Online method is good at complex textures. The reason is two folds. Firstly, the Offline method is learned on clean images and hence is better at representing edges, structuals, and smooth area. The online method is influenced by the noise and hence some noise cannot be removed. Secondly, the Online method is better at recovering complex area sicne they could learn adaptive dictionaries for the specific area. The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.

\begin{table}\label{tab1}
\caption{Average PSNR(dB) results of External, Internal, and Guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
\vspace{-2mm}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Guided}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9691}
%\\
%\hline
\end{tabular}
\end{center}\vspace{-4mm}
\end{table}

@@

\subsection{Comparison with Other Denoising Methods}
We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}. We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.  The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly. All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image. The NeatImage will fail to perform automatical parameters settings if there is no uniform regions. \footnote{To compare with CCNoise, we first transform the denoised images into double format.}

@@

\clearpage
{
\small
\bibliographystyle{unsrt}
\bibliography{egbib}
}
